---
title: "Go Fish Explanation, Description, and Free Response"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(patchwork)
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```



```{r globals, include=FALSE}
# Data files
ROUND1_SUMMARY_DATA = "round1/01_go_fish_meta.csv"
ROUND1_TRIAL_DATA = "round1/02_go_fish_trials.csv"
ROUND1_GENERATION_RESP_DATA = "round1/03_go_fish_generation_free_resp.csv"
ROUND1_GENERATION_JUDG_DATA = "round1/04_go_fish_generation_judgment.csv"
ROUND1_EVAL_DATA = "round1/05_go_fish_evaluation.csv"
ROUND1_MEMORY_DATA = "round1/06_go_fish_memory.csv"

ROUND2_SUMMARY_DATA = "round2/01_go_fish_meta.csv"
ROUND2_TRIAL_DATA = "round2/02_go_fish_trials.csv"
ROUND2_GENERATION_RESP_DATA = "round2/03_go_fish_generation_free_resp.csv"
ROUND2_GENERATION_JUDG_DATA = "round2/04_go_fish_generation_judgment.csv"
ROUND2_EVAL_DATA = "round2/05_go_fish_evaluation.csv"
ROUND2_MEMORY_DATA = "round2/06_go_fish_memory.csv"

GENERATION_RESP_DATA_CODED = "free_response_combined.csv"
```



```{r analysis_fxn, include=FALSE}
# Read in and process summary data file
read_summary_data = function(filepath, is_round1) {
  # Read in data at filepath and add/modify columns as needed
  summary_data = read_csv(filepath)
  summary_data = summary_data %>%
    mutate(Condition = ifelse(is_control == TRUE, "Describe", "Explain"),
           Round1 = is_round1,
           experiment_completion_time = (expt_end_ts - expt_start_ts) / 1000)
  return(summary_data)
}

# Read in and process data from explain/describe trials
read_trial_data = function(filepath, is_round1) {
  trial_data = read_csv(filepath)
  trial_data = trial_data %>%
    mutate(
      Condition = ifelse(is_control == TRUE, "Describe", "Explain"),
      Round1 = is_round1,
      input_correct =
        (input_prediction_catches_fish == prediction_catches_fish))
  trial_data$input_evidence_response = str_replace_all(
    trial_data$input_evidence_response, "\n" , "[newline]")
  return(trial_data)
}

# Read in coded free response data (note this requires writing free response data to csv in initialization code)
read_coded_free_resp_data = function(filename, summary_data) {
  generation_free_resp_coded = read_csv(filename)
  generation_free_resp_coded = generation_free_resp_coded %>%
    select(subjID, free_response_str, Revision) %>%
    inner_join(., summary_data, by = "subjID") %>%
    select(subjID, Condition, free_response_str, Revision)
  
  return(generation_free_resp_coded)
}

# Read in and process data from generation "judgment" (binary response) task
read_generation_judgment_data = function(filepath, is_round1) {
  generation_judgment_data = read_csv(filepath)
  generation_judgment_data = generation_judgment_data %>%
    mutate(
      Condition = ifelse(is_control == TRUE, "Describe", "Explain"),
      Round1 = is_round1,
      input_correct = 
        (input_judgment == judgment_catches_fish))
  return(generation_judgment_data)
}

# Summarize generation judgment data by participant
get_generation_judgment_subj_summary = function(generation_judgment_data) {
  generation_subject_summary = generation_judgment_data %>%
    group_by(Condition, subjID) %>%
    summarize(subj_accuracy = sum(input_correct) / n())
  return(generation_subject_summary)
}

```



```{r data, include=FALSE}
# Read in data
summary_data = bind_rows(read_summary_data(ROUND1_SUMMARY_DATA, TRUE), 
                         read_summary_data(ROUND2_SUMMARY_DATA, FALSE))
trial_data = bind_rows(read_trial_data(ROUND1_TRIAL_DATA, TRUE),
                       read_trial_data(ROUND2_TRIAL_DATA, FALSE))
generation_free_resp_coded = read_coded_free_resp_data(GENERATION_RESP_DATA_CODED, summary_data)
generation_judgment_data = bind_rows(read_generation_judgment_data(ROUND1_GENERATION_JUDG_DATA, TRUE),
                                     read_generation_judgment_data(ROUND2_GENERATION_JUDG_DATA, FALSE))

# Summarize data as needed
generation_judgment_subject_summary = get_generation_judgment_subj_summary(generation_judgment_data)
```



# Summary
This document is intended for easy review and analysis of participant free response data. 

We display participant explanations and descriptions during the evidence phase of the experiment, as well as explicit hypotheses from the free response hypothesis generation task. 



# Explanations

Below we list each subject's trial explanations ordered by trial index (1-8), along with whether they ultimately generated the correct hypothesis and what their final accuracy was on the hypothesis discrimination task.

```{r explanations, echo=FALSE}

explanation_data = generation_free_resp_coded %>%
  select(subjID, Condition, Revision) %>%
  filter(Condition == "Explain") %>%
  inner_join(., trial_data, by = c("subjID", "Condition")) %>%
  inner_join(., generation_judgment_subject_summary, by = c("subjID")) %>%
  select(subjID, trial_index, input_evidence_response, Revision, subj_accuracy) %>%
  arrange(subjID, trial_index)


kable(explanation_data,
      col.names = c("Subject ID", "Trial", "Explanation", "Hyp. Gen. Correct", "Hyp. Gen. Accuracy"))

```



# Descriptions

Below we list each control subject's trial descriptions ordered by trial index (1-8), along with whether they ultimately generated the correct hypothesis and what their final accuracy was on the hypothesis discrimination task.

```{r descriptions, echo=FALSE}

description_data = generation_free_resp_coded %>%
  select(subjID, Condition, Revision) %>%
  filter(Condition == "Describe") %>%
  inner_join(., trial_data, by = c("subjID", "Condition")) %>%
  inner_join(., generation_judgment_subject_summary, by = c("subjID")) %>%
  select(subjID, trial_index, input_evidence_response, Revision, subj_accuracy) %>%
  arrange(subjID, trial_index)


kable(explanation_data,
      col.names = c("Subject ID", "Trial", "Description", "Hyp. Gen. Correct", "Hyp. Gen. Accuracy"))

```



# Hypothesis Generation: Free Response Data

Below we list each subject's hypothesis generation free response, along with whether it was coded as correct

```{r free_resp, echo=FALSE}

free_resp_summary = generation_free_resp_coded %>%
  inner_join(., generation_judgment_subject_summary, by = c("subjID", "Condition")) %>%
  select(subjID, Condition, free_response_str, Revision, subj_accuracy) %>%
  arrange(Condition, subjID)

kable(free_resp_summary,
      col.names = c("Subject ID", "Condition", "Hypothesis", "Correct", "Judgment Task Accuracy"))
```



